l

### 2024-08-13 resume/Resume.tex
Deploying to gh-pages from @ JasonGross/JasonGross.github.io@3f47a114b1f4a4215d649df0dfdf1074921ed186 🚀
Deploying to gh-pages from @ JasonGross/JasonGross.github.io@b0a221edd069d45e659ded594349a8e2a9a4df17 🚀
Deploying to gh-pages from @ JasonGross/JasonGross.github.io@f514aa8cdd283c872edc741b5d54be969118930c 🚀
Deploying to gh-pages from @ JasonGross/JasonGross.github.io@f133da88691b0bb5f0833d3abdde9d071cc038aa 🚀

\usepackage[T1]{fontenc}
\usepackage[margin=1in,top=0.5in,bottom=0.5in]{geometry}
\usepackage{hyperref}
\usepackage{calc}
\usepackage{amsmath}
\usepackage{etoolbox}[2011/01/03]
\expandafter\def\csname blx@noerroretextools\endcsname{}
\usepackage[backend=biber,maxbibnames=99,sorting=ymdnt,style=alphabetic]{biblatex}
% http://tex.stackexchange.com/a/140641
\DeclareSortingTemplate{ymdnt}{
    \sort{
        \field{presort}
    }
    \sort[final]{
        \field{sortkey}
    }
    \sort[direction=descending]{
        \field{sortyear}
        \field{year}
        \literal{9999}
    }
    \sort[direction=descending]{
        \field[padside=left,padwidth=2,padchar=0]{month}
        \literal{99}
    }
    \sort[direction=descending]{
        \field[padside=left,padwidth=2,padchar=0]{day}
        \literal{99}
    }
    \sort{
        \field{sortname}
        \field{author}
        \field{editor}
        \field{translator}
        \field{sorttitle}
        \field{title}
    }
    \sort{
        \field{sorttitle}
        \field{title}
    }
}
\addbibresource{jason-gross.bib}
\DeclareBibliographyCategory{exclude}
\makeatletter
\@ifpackageloaded{etextools}{%
}{%
  \let\origifempty\ifempty
  \let\origforlistloop\forlistloop
  \undef\ifempty
  \usepackage{etextools}
  \let\eifempty\ifempty
  \let\ifempty\origifempty
  \let\forlistloop\origforlistloop
  \def\preetextools{\let\ifempty\eifempty}
}%
\makeatother
\begin{format}
  \employer{l}\dates{r}\\
  \title{l}\location{r} \\
  \body
\end{format}
\let\oldemployer=\employer
\let\oldtitle=\title
\renewcommand{\employer}[1]{\oldemployer{\textbf{#1}}}
\renewcommand{\title}[1]{\oldtitle{\textit{#1}}}

@@

%\section{\textsc{Research Interests}}
%\begin{itemize}
%\item AI: Mechanistic Interpretability, Heuristic Arguments, Compact Proofs, Löb's Theorem
%\item Security \& Engineering: Formal Verification, Cryptography, Bugs \& CI Infrastructure
%\item Programming Languages: Type Theory, Performance, Proof Engines \& Automation
%%
%%\item Mechanistic Interpretability: Heuristic Arguments, Compact Proofs, Type Theory
%%\item Security Engineering: Formal Verification, Cryptography, Performance Engineering
%%\item Programming Languages and AI: Löb's Theorem, Type Theory, Compact Proof Generation
%%%\item Trust and Security Engineering: Formal Verification, Cryptography, Performance Engineering
%\end{itemize}
\section{\textsc{About Me}}
\vspace*{-0.25cm}
I'm a programming languages research scientist transitioning into ML and alignment.
I have a working knowledge of around two dozen programming languages, and expertise in a handful (Coq ($\approx$1M+ loc), Python ($\approx$50k loc), Agda ($\approx$50k loc), others).
I spent my PhD on low-level cryptographic code generation, proof automation, performance engineering, and infrastructure around debugging and CI.
My current project is in mechanistic interpretability, heuristic arguments, and compact proofs.
I'm excited about what scalable performant automation can make possible.

@@

\employer{Special Project of ARC Theory}
\dates{August 2023--Present}
\title{Project Lead}
\location{Berkeley, CA}
\begin{position}
  \begin{itemize}
  \item Building the first machine-checked functional-correctness proofs of mechanistic interpretability arguments about transformers in Coq (\href{https://github.com/JasonGross/neural-net-coq-interp}{\texttt{github.com/JasonGross/neural-net-coq-interp}})
  \item Raised \$150k and leading an interdisciplinary team of ML researchers and mathematicians
  \end{itemize}
\end{position}

\employer{\mbox{Machine Intelligence Research Institute (MIRI)}}
\dates{February 2021--Present}
\title{Research Staff}
\location{Berkeley, CA (remote)}
\begin{position}
  \begin{itemize}
  \item Performing self-directed research into fundamental programming language theory and math%ematics%, bringing insights and understanding back to my supervisor
  \end{itemize}
\end{position}

@@

\clearpage
\section{\textsc{Selected Presentations and Publications}}
\addtocategory{exclude}{Evaluation2021Huhmann}
\printbibliography[title={$\left.\right.$},notcategory=exclude]

>>>>

\usepackage[T1]{fontenc}
\usepackage[margin=1in,top=0.5in,bottom=0.5in]{geometry}
\usepackage{hyperref}
\usepackage{calc}
\usepackage{amsmath}
\usepackage{etoolbox}[2011/01/03]
\let\origifempty\ifempty
\let\origforlistloop\forlistloop
\undef\ifempty
\usepackage{etextools}
\let\eifempty\ifempty
\let\ifempty\origifempty
\let\forlistloop\origforlistloop
\expandafter\def\csname blx@noerroretextools\endcsname{}
\usepackage[backend=biber,maxbibnames=99,sorting=ymdnt,style=alphabetic]{biblatex}
% http://tex.stackexchange.com/a/140641
\DeclareSortingTemplate{ymdnt}{
    \sort{
        \field{presort}
    }
    \sort[final]{
        \field{sortkey}
    }
    \sort[direction=descending]{
        \field{sortyear}
        \field{year}
        \literal{9999}
    }
    \sort[direction=descending]{
        \field[padside=left,padwidth=2,padchar=0]{month}
        \literal{99}
    }
    \sort[direction=descending]{
        \field[padside=left,padwidth=2,padchar=0]{day}
        \literal{99}
    }
    \sort{
        \field{sortname}
        \field{author}
        \field{editor}
        \field{translator}
        \field{sorttitle}
        \field{title}
    }
    \sort{
        \field{sorttitle}
        \field{title}
    }
}
\addbibresource{jason-gross.bib}
\DeclareBibliographyCategory{exclude}
\begin{format}
  \employer{l}\dates{r}\\
  \title{l}\location{r} \\
  \body
\end{format}
\let\oldemployer=\employer
\let\oldtitle=\title
\renewcommand{\employer}[1]{\oldemployer{\textbf{#1}}}
\renewcommand{\title}[1]{\oldtitle{\textit{#1}}}

@@

%\section{\textsc{Research Interests}}
%\begin{itemize}
%\item AI: Mechanistic Interpretability, Heuristic Arguments, Compact Proofs, Löb's Theorem
%\item Security \& Engineering: Formal Verification, Cryptography, Bugs \& CI Infrastructure
%\item Programming Languages: Type Theory, Performance, Proof Engines \& Automation
%%
%%\item Mechanistic Interpretability: Heuristic Arguments, Compact Proofs, Type Theory
%%\item Security Engineering: Formal Verification, Cryptography, Performance Engineering
%%\item Programming Languages and AI: Löb's Theorem, Type Theory, Compact Proof Generation
%%%\item Trust and Security Engineering: Formal Verification, Cryptography, Performance Engineering
%\end{itemize}
\section{\textsc{About Me}}
\vspace*{-0.25cm}
I'm a programming languages research scientist transitioning into ML and alignment.
I have a working knowledge of around two dozen programming languages, and expertise in a handful (Coq ($\approx$1M+ loc), Python ($\approx$80k loc), Agda ($\approx$50k loc), others).
I spent my PhD on low-level cryptographic code generation, proof automation, performance engineering, and infrastructure around debugging and CI.
My current project is in mechanistic interpretability, heuristic arguments, and compact proofs.
I'm excited about what scalable performant automation can make possible.

@@

\employer{Special Project of ARC Theory}
\dates{August 2023--Present}
\title{Project Lead}
\location{Berkeley, CA}
\begin{position}
  \begin{itemize}
  \item Building the first machine-checked functional-correctness proofs of mechanistic interpretability arguments about transformers in Coq (\href{https://github.com/JasonGross/neural-net-coq-interp}{\texttt{github.com/JasonGross/neural-net-coq-interp}})
  \item Raised \$150k \& leading an interdisciplinary team of eight ML researchers and mathematicians
  \end{itemize}
\end{position}

\employer{\mbox{Machine Intelligence Research Institute (MIRI)}}
\dates{February 2021--September 2023}
\title{Research Staff}
\location{Berkeley, CA (remote)}
\begin{position}
  \begin{itemize}
  \item Performing self-directed research into fundamental programming language theory and math%ematics%, bringing insights and understanding back to my supervisor
  \end{itemize}
\end{position}

@@

\clearpage
\section{\textsc{Selected Presentations and Publications}}
\addtocategory{exclude}{Evaluation2021Huhmann}
\printbibliography[title={\ensuremath{\left.\right.}},notcategory=exclude]
